---
title: "tidymodels_1"
author: "Lazaro Alonso"
date: "6/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Unsupervised Learning
Genral goal: Design an app in which you can upload a picture from your computer or a link and afterwards apply 
`k-means` clustering to find out the most dominant colours in that picture. 

### K-means clustering 
LEARNING OBJECTIVE
Summarize clustering characteristics and estimate the best number of clusters for a data set.

- `tidy()`
- `augment()`
- `glance()`

```{r}
library(tidymodels)
library(tidyverse)

set.seed(27)

centers <- tibble(
  cluster = factor(1:3), 
  num_points = c(100, 150, 50),  # number points in each cluster
  x1 = c(5, 0, -3),              # x1 coordinate of cluster center
  x2 = c(-1, 1, -2)              # x2 coordinate of cluster center
)
centers 
```

Generar los puntos 

```{r}
?map2
```


```{r}
labelled_points <- 
  centers %>%
  mutate(
    x1 = map2(num_points, x1, rnorm),
    x2 = map2(num_points, x2, rnorm)
  ) %>% 
  select(-num_points) %>% 
  unnest(cols = c(x1, x2))
labelled_points
```
```{r}
ggplot(labelled_points, aes(x1, x2, color = cluster)) +
  geom_point(alpha = 0.5) + theme_minimal()
```
We’ll use the built-in `kmeans()` function, which accepts a data frame with all numeric columns as it’s primary argument.


```{r}
points <- 
  labelled_points %>% 
  select(-cluster)
points
```
```{r}
kclust <- kmeans(points, centers = 3)
kclust
```
`augment` adds the point classifications to the original data set:

```{r}
augment(kclust, points)
```
```{r}
tidy(kclust)
```
The `glance()` function extracts a single-row summary:

```{r}
glance(kclust)
```
### EXPLORATORY CLUSTERING

```{r}
kclusts <- 
  tibble(k = 1:9) %>%
  mutate(
    kclust = map(k, ~kmeans(points, .x)),
    tidied = map(kclust, tidy),
    glanced = map(kclust, glance),
    augmented = map(kclust, augment, points)
  )

kclusts
```
```{r}
clusters <- 
  kclusts %>%
  unnest(cols = c(tidied))

assignments <- 
  kclusts %>% 
  unnest(cols = c(augmented))

clusterings <- 
  kclusts %>%
  unnest(cols = c(glanced))

```

```{r}
clusterings
```



```{r}
ggplot(clusterings, aes(k, tot.withinss)) +
  geom_line() + geom_point() + 
  geom_vline(xintercept = 3, color = "orange", size = 0.5)
```
This represents the variance within the clusters. It decreases as k increases, but notice a bend (or “elbow”) around k = 3. This bend indicates that additional clusters beyond the third have little value.

- https://web.stanford.edu/~hastie/Papers/gap.pdf
